Multi-Label Speech Emotion Recognition Using 2D Convolutional Neural Networks

### 2019-09-09 research/paper/paper_header.tex
Update paper with revisions and improvements

\begin{abstract}
Current speech emotion recognition systems often overlook the multi-label data that comes with databases. In this paper, we address the problem of whether machine learning can be used to detect multiple emotions in speech. We created a combined database consisting of four speech emotion-labeled databases, and we used it to train a 2D convolutional neural network to determine if the model could recognize multiple emotions in a speech sample. The model was able to classify the samples with an accuracy of 57.64\%. This shows that it is possible to apply machine learning to the problem of multi-label speech emotion recognition and to achieve a reasonable accuracy.\footnote{Code for this paper is available on Github at: \url{https://github.com/Brian-Pho/RVST598_Speech-Emotion-Recognition}}
\end{abstract}

>>>>

\begin{abstract}
A problem with current speech emotion recognition systems is that they can only recognize one emotion from a set of emotions in speech. This is a problem because it does not match how people recognize emotions in speech. When people hear speech, they can perceive multiple emotions instead of a single emotion. We address this problem by building a 2D convolutional neural network that can also recognize multiple emotions and it achieves an accuracy of 57.64\%. This model demonstrates a more realistic approach to speech emotion recognition by more closely matching human data.\footnote{Code for this paper is available on Github at: \url{https://github.com/Brian-Pho/RVST598_Speech-Emotion-Recognition}}
\end{abstract}
